%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Data Service Engineer} % Job title
{Dataspark Pte. Ltd.} % Organization
{Jakarta, Indonesia.} % Location
{Aug. 2019 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Deliver big data pipelines (ETL) for Dataspark's patented Mobility Analytics software.}
    \item {Deliver big data pipelines (ETL) for Dataspark's patented Network Planning Optimiser software.}
    \item {Sales/Pre-Sales support for Telco data acquisition and verification.}
    \item {Operational support and maintenance for Dataspark's product running on customer's data lake.}
    \item {Acting as internal scrum master for Service Engineering division on roster basis.}
    
    Tech Stack : Apache Hadoop, Spark, Scala, Python, Go
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Senior System Engineer} % Job title
    {Packet Systems Indonesia} % Organization
    {Jakarta, Indonesia} % Location
    {Jul. 2016 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team leader for Cisco Prime OSS for Mobile Packet Core nodes.}
        \item {Develop ad-hoc monitoring suite by combining open source software, inhouse-developed log parser, and statistic data based on networking devices' command-line interface output.}
        \item {Develop ad-hoc scripts to automate periodic performance data collection.}
        \item {Sales/Pre-Sales support for packet core network data munging and analytics.}
        \item {Sales/Pre-Sales support for network troubleshooting using raw packet capture analysis taken from mobile network interfaces.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Engineer \& DevOps} % Job title
    {Niometrics} % Organization
    {Jakarta, Indonesia} % Location
    {May. 2015 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solution engineering of Niometrics project in major Southeast Asia telco operators.}
        \item {Supporting developers on software release cycles and quality assurance.}
        \item {Supporting Account/Project manager team on adhoc data analysis and reporting.}
        \item {Subject Matter Expert on IP networking and packet-switched core network technologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Integration Engineer} % Job title
    {Ericsson} % Organization
    {Jakarta, Indonesia} % Location
    {Sep. 2012 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integration engineer for WiFi offload trial, LTE Trial, Policy and Charging migration, M2M platform, and capacity expansion in XL Axiata.}
        \item {Supporting Interoperability Test \& Multi Vendor Verification between Ericsson, Huawei, Amdocs.}
        \item {Creating ad-hoc shell scripts to help monitor Network Element's statistics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer} % Job title
    {Multipolar Technology} % Organization
    {Jakarta, Indonesia} % Location
    {May. 2011 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solution design and sales support for multi-million USD project tender in Bank Indonesia, British Petroleum, Taspen, Telkomsel.}
        \item {Post-Sales support for Office IT Network expansion at Telkomsel, WAN optimization at Commbank Indonesia, and IDX Disaster Recovery network.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
